### 2015-02-28 icfp15-servo/open.tex
nit
More open problems

\section{Open}
\label{sec:open}
While this work has discussed many challenges in browser design and our current progress,
there are many other interesting open problems.

@@

>>>>

\section{Open problems}
\label{sec:open}
While this work has discussed many challenges in browser design and our current progress,
there are many other interesting open problems.

@@

\paragraph{Unsafe code correctness.} Today, when we write unsafe code in Rust
there is limited validation of memory lifetimes or type safety within that
code block.
However, many of our uses of unsafe code are well-behaved pointer lifetime
or memory translations that cannot be annotated or inferred in Rust.
We are very interested in additional annotations that would help us prove
basic properties about our unsafe code, even if these annotations require a
theorem prover or ILP solver to check.

\paragraph{Incremental computation.} As mentioned in \secref{sec:browsers},
all modern browsers use some combination of dirty bit marking and incremental
recomputation heuristics to avoid reprocessing the full page when
the state is mutated.
Unfortunately, these heuristics are not only frequently the source of
performance differences between browsers, but they are also a source of
correctness bugs.
A library that provided a form of self adjusting computation suited to
incremental recomputation of only the visible part of the page, perhaps
like the work on Adapton~\cite{adapton}, seems like a promising
approach to addressing this problem.
